Plotting plots and Hotzenplotz

### 2024-11-04 plotting1.Rmd
plotting1start

---
title: "1-Define Data"
author: "Verooo"
date: "2024-11-01"
output: html_document
---

@@

```{r klippy, echo=FALSE, include=FALSE}
klippy::klippy(position = c('top', 'right'))
klippy::klippy(color = 'darkred')
klippy::klippy(tooltip_message = 'Click to copy', tooltip_success = 'Done')
```

@@

@@

[**Defining Data**]{.underline}

# Before the start

## Clean workspace

```{r}
# start with clean workspace
rm(list = ls())

```{r}
# install.packages('tidyverse')
require(tidyverse)

# install an old version of RSiena including sienaRI
#remove.packages("RSiena") #use this to remove the current version of RSiena
#devtools::install_version("RSiena", version = "1.3.14", repos = "C:/Users/Vero/OneDrive - Radboud Universiteit/Documents/GitHub/labjournal") # This installs an older version

# Run R as administrator when you install the older version!!

# You should end up with version 1.3.14 loaded in instead of 1.4.7, 
# but then make sure there isn't a install.packages("RSiena") function running somewhere, because then it will reinstall the newest version

require(RSiena)
require(RsienaTwoStep)

I do not seem to be able to call on the package RSiena, nor can I reinstall it.... I know programming never works on the first try but... goddamnit, why not even after 15?

## Functions

### Question

**HOW do I get the discipline of political science in there too?**

**How can I find out what the name for the discipline of political science in the original data frame (e.g. whether it is called polsci, political science, or politicalscience)?**

**I don't know how to view the data set BEFORE we include only those scholars that have discipline = sociology. I cannot view the data**

I tried removing the discipline = "sociology" part in the f_pubnets, fcolnet and all following functions that select data BUT SINCE 'discipline' is also relevant in the rest of the functions' code, it does not end up doing what I hoped (having a dataset with scholars of no specific discipline because then I could hopefully check how the department is named in the data and then find out how to add that to the data set initially).

```{r}
fpackage.check <- function(packages) {
    lapply(packages, FUN = function(x) {
        if (!require(x, character.only = TRUE)) {
            install.packages(x, dependencies = TRUE)
            library(x, character.only = TRUE)
        }
    })
}

@@

## more functions

```{r}
fcolnet <- function(data = scholars, university = "RU", discipline = "sociology"+"political science", waves = list(c(2015,
    2018), c(2019, 2023)), type = c("first")) {

@@

    if (type == "all") {
        for (j in 1:nwaves) {
            df_works_w <- df_works[df_works$works_year >= waves[[j]][1] & df_works$works_year <= waves[[j]][2],
                ]
            for (i in 1:nrow(df_works_w)) {
                egos <- df_works_w$works_author[i][[1]]$au_id
                if (sum(ids %in% egos) > 0) {
                  nets[j, which(ids %in% egos), which(ids %in% egos)] <- 1
                }
            }
        }
    }
    output <- list()
    output$data <- scholars_sel
    output$nets <- nets
    return(output)
}

@@

## load and inspect data

#inspecting scholars_20240924.rda object
#df_ego <- do.call(rbind.data.frame, scholars$demographics)
#unique(df_ego$discipline.22)

# save the output of your function
testsoc  <- fcolnet(data = scholars, 
                university = "RU", 
                discipline = "sociology", 
                waves = list(c(2015, 2018), c(2019, 2023)),

@@

------------------------------------------------------------------------

# Define Data

## waves - sociology department

@@

## QUESTION:

HOW COME: when I "correct" Jochem and put [rows,columns,waves] instead of [waves, rows, columns], the sienaDependent function does not work, but it DOES work if I leave the "incorrect" version unchanged?!

## waves - polsci department

@@

### **(old) QUESTION:**

**What's the difference between putting the 2 and the 1 at the dimensions. I feel like one is appropriate since I am only looking at one wave, not two, but since the output is among the 'values' not 'data', I cannot view the variable net_soc_array(1) nor "visualize" what that means in terms of its structure. I don't really know what the difference would be between the 1:2 and the 1 in the outputs, structurally.**

### ANSWER:

RSiena needs at least two waves, because it models the evolution of the networks. We have to store the networks in an array before we can convert it to an dependent variable objects. Moreover, for RSiena the dimensions should be in the following order: rows, columns, waves.

I 'messed up' my function (for didactic reasons ;-) )and stored the nets in the following order: waves, rows, columns. Thus, either correct my function or retrieve the separate waves and store them in the order RSiena requires.

## (new) QUESTION:

We had agreed on me only investigating one time point for the sake of simplicity. It seems I basically have no choice but to investigate two waves, revisit my RQs and make an additional RQ about tie changes over time, right?

Then I would end up with 4 RQs and that seems like more than it needs to be for this project (great for a research incentive, but for this class I need to keep it simple, as I am currently very overworked).

Any advice on how I can keep it simple, nonetheless?

## Examine structure

```{r}
dim(testsoc$nets)
```

```{r}
dim(testpolsci$nets)
```

## My data

### sociology dep.

@@

  # --> EGO DATAFRAME with demo and oa (sociology)
  ?join.data.frame
  df_soc_ego <- left_join(df_ego_demo, df_ego_oa, by = join_by(au_id == id))

@@

### polsci department

@@

## Gender

### gender-soc

@@

### gender - polsci

@@

### joining polsci and soc data

```{r}
df_both_ego <- full_join(df_soc_ego, df_pol_ego, by = join_by
                    (au_id == au_id, 
                     Naam==Naam, 
                     gender == gender, 
                     discipline.22 == discipline.22,
                     discipline.24 == discipline.24,
                     counts_by_year== counts_by_year, 
                     works_count == works_count, 
                     cited_by_count == cited_by_count, 
                     Universiteit1.22 == Universiteit1.22,
                     Universiteit2.22 == Universiteit2.22,
                     Universiteit1.24 == Universiteit1.24,
                     Universiteit2.24 == Universiteit2.24,
                     Universiteit.22 == Universiteit.22, 
                     Universiteit.24 == Universiteit.24,
                     no_oa_id == no_oa_id,
                     display_name == display_name,
                     display_name_alternatives == display_name_alternatives,
                     ids== ids,
                     orcid == orcid,
                     year.22 == year.22,
                     year.24 == year.24,
                     Functie.24== Functie.24,
                     relevance_score == relevance_score,
                     affiliation_display_name == affiliation_display_name,
                     affiliation_ror == affiliation_ror,
                     affiliation_id == affiliation_id,
                     affiliation_country_code == affiliation_country_code,
                     affiliation_type == affiliation_type,
                     affiliations_other == affiliations_other,
                     affiliation_lineage == affiliation_lineage,
                     Specialisatie.22 == Specialisatie.22,
                     Specialisatie.24 == Specialisatie.24,
                     x_concepts == x_concepts,
                     works_api_url == works_api_url))
# 101 scholars (50 sociology + 51 polsci) and 43 variables (as opposed to 21 bc i could not join them all.)

@@

## QUESTION:

With 101 scholars, instead of the nr. of scholars of looking at just one department, I wonder if this is where we could simplify. Looking at a change over time, but not looking through a lens that wants to compare the two departments. Instead, I could just look at one department.

What do you think?

## H-index webscraping

@@

## Actually define data:

### RSiena troubleshooting

(Cannot install RSiena for some reason.)

```{r}
#require(RSiena)
#require(RsienaTwoStep)
```

Changed administration rights in properties to get around the "file not found"-error.

```{r}
# dependent:
# net <- sienaDependent(net_soc_array) # Does not work "need 2 node sets for a bipartite network"

#also this is only the array for sociology, I need to have a combined DV for both departments for RQ1 ...

# str(net_soc_array)
# my output here: 1:2, 1:50, 1:2
# but in week 5-2: 1:50, 1:50, 1:2

# net <- sienaDependent(net_soc_array) # Which array to take

#covariate 1
# gender <- coCovar(df_ego$gender)
# covariate 2
# h_index <- coCovar(df_ego$h_index)

#combining data: wish I knew of this shit earlier...
# mydata <- sienaDataCreate(net, gender)
```

# Create effects structure

```{r}
#myeff <- getEffects(mydata)
```

>>>>

---
title: "Plotting plots and Hotzenplotz"
author: "Verooo"
date: "2024-11-04"
output: html_document
---

@@

```{r klippy, echo=FALSE, include=FALSE}
klippy::klippy(position = c('top', 'right'))
#klippy::klippy(color = 'darkred')
#klippy::klippy(tooltip_message = 'Click to copy', tooltip_success = 'Done')
```

@@

```
# Set-up
## Clean workspace
```{r}
rm(list = ls())
```

```{r}
require(tidyverse)
require(RSiena)
require(RsienaTwoStep)

#install.packages("data.table")
require(data.table)  # mainly for faster data handling
# install.packages('xml2')
require(xml2)
# install.packages('rvest')
require(rvest)
require(igraph)

require(ggraph)
#install.packages('visNetwork')
require(visNetwork)
#install.packages('threejs')
require(threejs)
#install.packages('networkD3')
require(networkD3)

@@

## Functions 
```{r}
fpackage.check <- function(packages) {
    lapply(packages, FUN = function(x) {
        if (!require(x, character.only = TRUE)) {
            install.packages(x, dependencies = TRUE)
            library(x, character.only = TRUE)
        }
    })
}

@@

## More functions 
```{r}
fcolnet <- function(data = scholars, university = "RU", discipline = "sociology"+"political science", waves = list(c(2015,
    2018), c(2019, 2023)), type = c("first")) {

@@

    if (type == "all") {
        for (j in 1:nwaves) {
            df_works_w <- df_works[df_works$works_year >= waves[[j]][1] & df_works$works_year <= waves[[j]][2],
                ]
            for (i in 1:nrow(df_works_w)) {
                egos <- df_works_w$works_author[i][[1]]$au_id
                if (sum(ids %in% egos) > 0) {
                  nets[j, which(ids %in% egos), which(ids %in% egos)] <- 1
                }
            }
        }
    }
    output <- list()
    output$data <- scholars_sel
    output$nets <- nets
    return(output)
}
```

## Load data

@@

```{r}
# save the output of your function
testsoc  <- fcolnet(data = scholars, 
                university = "RU", 
                discipline = "sociology", 
                waves = list(c(2015, 2018), c(2019, 2023)),

@@

### waves - sociology department

@@

### waves - polsci department

@@

### My data

#### sociology dep.

@@

  # --> EGO DATAFRAME with demo and oa (sociology)
  # ?join.data.frame
  df_soc_ego <- left_join(df_ego_demo, df_ego_oa, by = join_by(au_id == id))

@@

#### polsci department

@@

### Gender

#### gender-soc

@@

#### gender - polsci

@@

### joining soc and polsci data
```{r}
df_both_ego <- full_join(df_soc_ego, df_pol_ego, by = join_by
                    (au_id == au_id, 
                     Naam==Naam, 
                     gender == gender, 
                     discipline.22 == discipline.22,
                     discipline.24 == discipline.24,
                     counts_by_year== counts_by_year, 
                     works_count == works_count, 
                     cited_by_count == cited_by_count, 
                     Universiteit1.22 == Universiteit1.22,
                     Universiteit2.22 == Universiteit2.22,
                     Universiteit1.24 == Universiteit1.24,
                     Universiteit2.24 == Universiteit2.24,
                     Universiteit.22 == Universiteit.22, 
                     Universiteit.24 == Universiteit.24,
                     no_oa_id == no_oa_id,
                     display_name == display_name,
                     display_name_alternatives == display_name_alternatives,
                     ids== ids,
                     orcid == orcid,
                     year.22 == year.22,
                     year.24 == year.24,
                     Functie.24== Functie.24,
                     relevance_score == relevance_score,
                     affiliation_display_name == affiliation_display_name,
                     affiliation_ror == affiliation_ror,
                     affiliation_id == affiliation_id,
                     affiliation_country_code == affiliation_country_code,
                     affiliation_type == affiliation_type,
                     affiliations_other == affiliations_other,
                     affiliation_lineage == affiliation_lineage,
                     Specialisatie.22 == Specialisatie.22,
                     Specialisatie.24 == Specialisatie.24,
                     x_concepts == x_concepts,
                     works_api_url == works_api_url))
# 101 scholars (50 sociology + 51 polsci) and 43 variables (as opposed to 21 bc i could not join them all.)

@@

### H-index webscraping

@@

# Plots and such 
## wave 1 - soc
```{r}
testsoc_w1 <- igraph::graph_from_adjacency_matrix(
  testsoc$nets[1,,], # first wave of data. 
  # (thus I select the array of networks and take the first matrix)
  mode = c("directed"),
  weighted = NULL,
  diag = FALSE,
  add.colnames = NULL,
  add.rownames = NULL
)

plot(testsoc_w1,
     vertex.label = NA,
     edge.width = 0.2,
     edge.arrow.size =0.2)

```
## wave 2 - soc
```{r}
testsoc_w2 <- igraph::graph_from_adjacency_matrix(
  testsoc$nets[2,,], #take the second wave 
  mode = c("directed"),
  weighted = NULL,
  diag = FALSE,
  add.colnames = NULL
  )

plot(testsoc_w2,
     vertex.label = NA,
     edge.width = 0.2,
     edge.arrow.size =0.2)
```

## wave 1 - pol
```{r}
testpol_w1 <- igraph::graph_from_adjacency_matrix(
  testpolsci$nets[1,,], #for this example I take the first wave of data. (thus I select the array of networks and take the first matrix)
  mode = c("directed"),
  weighted = NULL,
  diag = FALSE,
  add.colnames = NULL,
  add.rownames = NULL
  )

plot(testpol_w1,
     vertex.label = NA,
     edge.width = 0.2,
     edge.arrow.size =0.2)

## wave 2 - pol
```{r}
testpol_w2 <- igraph::graph_from_adjacency_matrix(
  testpolsci$nets[2,,], #take the second wave 
  mode = c("directed"),
  weighted = NULL,
  diag = FALSE,
  add.colnames = NULL
  )

plot(testpol_w2,
     vertex.label = NA,
     edge.width = 0.2,
     edge.arrow.size =0.2)
```

##  Ego characteristics 
### soc ego
```{r, include=FALSE}
#Let us find ego characteristics. 
#first fish out the data
# df <- df_ego$data

#same complicated structure as 'scholars' thus first make a dataframe from the list in which all info was saved. 
# df_ego <- do.call(rbind.data.frame, df$demographics)
#DO NOT MESS UP THE ORDER! THUS IF YOU JOIN THIS DATA WITH YOUR OWN DATA CHECK THAT ORDER REMAINED THE SAME!!

# plot(test_w2,
     # vertex.color = ifelse(df_ego$Universiteit.24 == "RU", "red", "blue"), #now, I can use actor attributes for plotting. 
     # vertex.label = NA,
     # edge.width = 0.2,
     # edge.arrow.size =0.2)
```

### pol ego
```{r, include=FALSE}
#Let us find ego characteristics. 
#first fish out the data
# df <- testpolsci$data

#same complicated structure as 'scholars' thus first make a dataframe from the list in which all info was saved. 
# df_ego <- do.call(rbind.data.frame, df$demographics)
#DO NOT MESS UP THE ORDER! THUS IF YOU JOIN THIS DATA WITH YOUR OWN DATA CHECK THAT ORDER REMAINED THE SAME!!

# plot(test_w2,
#      vertex.color = ifelse(df_ego$Universiteit.24 == "RU", "red", "blue"), #now, I can use actor attributes for plotting. 
     # vertex.label = NA,
     # edge.width = 0.2,
     # edge.arrow.size =0.2)
```

# Descriptives 
```{r}
